NURM: a tool to locate numerical differences in pipelines

### 2019-05-17 paper.tex
Edited tool description

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}

\title{NURM-tool: a quantitative reproducibility measurement tool to 
identify numerical differences in pipelines}

@@

We present NURM-tool to automatically measure numerical reproducibility 
of the pipelines across operating systems (see 
Figures~\ref{fig:overview-cluster}, \ref{fig:overview-classify}). We build the 
containerized version of the pipelines for each operating system using 
docker technology which encapsulated whole the pipeline dependencies. 
The docker images consists of an specific computing environment such as 
operating system version, hardware configuration, software version, 
etc. Furthermore, to simplify computational reproducibility of the 
analysis, we execute docker images using Boutiques framework based on 
the command-line descriptions~\cite{glatard2017boutiques}. The 
Boutiques descriptor specifies the parameters and implementation of the 
experiment, and the invocation schema describes the parameter values 
such as input/output data path.

As shown in Figure~\ref{fig:overview-cluster}, NURM-tool clusters the 
input subjects into various types based on the similarity of their 
process trees which are achieved by \reprozip tool. 
Figure~\ref{fig:overview-classify} shows the iterative classification 
of the process based on the binary comparison of the outputs from 
various conditions. NURM-tool produces the \textit{difference} JSON 
schema in which recognizes output files with differences using the 
checksum comparison of the results. We consider that a file contains 
difference if only its binary comparison shows difference. Also, we use 
\reprozip tool to capture the provenance information. Subsequently, 
using a iterative approach, we classify processes into different 
categories regarding the state of read/write files with/without 
differences. NURM-tool identifies relevant processes in the pipeline 
creating, propagating, or removing differences. All the steps are 
explained in detail in the following sections.

\begin{figure}
  \centering
  \includegraphics[width=.7\columnwidth]{images/Slide1}
  \caption{An overview of the subject type clustering method.}
  \label{fig:overview-cluster}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.75\columnwidth]{images/Slide2}
  \caption{An overview of the process classification method.}
  \label{fig:overview-classify}
\end{figure}

%\begin{figure*}
%\centering
%    \begin{subfigure}{\columnwidth}
%        \includegraphics[width=\textwidth]{images/Slide1.png}
%        \caption{Subject clustering}
%        \label{fig:green}
%    \end{subfigure}
%\hfill%\hfil
%    \begin{subfigure}{\columnwidth}
%    \includegraphics[width=\textwidth]{images/Slide2.png}
%    \caption{Process classification}
%    \label{fig:red}
%\end{subfigure}
%    \caption{An overview of the proposed technique.}
%    \label{fig:processes}
%\end{figure*}

>>>>

\usepackage{subcaption}
\usepackage{xspace}

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\tristan}[1]{\color{blue}\textbf{From Tristan:}#1\color{black}}

\title{NURM: a tool to 
locate numerical differences in pipelines}

@@

Figure~\ref{fig:overview} shows an overview of our method.
For each tested condition, the
pipeline is containerized using Docker, and its interface is
described using Boutiques~\cite{glatard2017boutiques}. \reprozip
is added to the container images for provenance tracking. Our tool first
clusters the subjects based on the similarity of their process trees
produced by \reprozip (Fig.~\ref{fig:overview-cluster}). This results in a
reduced set of representative process trees to evaluate. The processes in
each representative process tree are labeled \tristan{Replace
``classification'' by ``labelling'' everyrwhere} from potential differences
found in their outputs produced in the tested conditions (Fig.~\ref{fig:overview-classify}).
To do that, a difference file is first produced that contains all the
files with differences across conditions
(Fig.~\ref{fig:overview-classify} - (A)\tristan{Add labels to the figure}).
Differences are identified simply by comparing file checksums. Using the
difference file, we then classify processes in 4 categories (Fig.~\ref{fig:overview-classify} - (B)) depending
whether they create differences (represented in red), remove differences
(blue), neither create nor remove differences (green), or have uncertain
behavior (yellow). When processes with an uncertain behavior are found, the
pipeline in condition 2 is modified (as explained later) and re-executed. This
procedure iterates until all processes are classified. 
\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=.7\columnwidth]{images/Slide1}
    \caption{Subject clustering.}
    \label{fig:overview-cluster}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=.75\columnwidth]{images/Slide2}
     \caption{Process classification.}
     \label{fig:overview-classify}
   \end{subfigure}
   \caption{Method overview}
   \label{fig:overview}
  \end{figure}
